Investigating the possible aspects affecting Canadian Individuals and Families' feelings about life

### 2022-03-20 output/paper3.Rmd
fix survey and others

---
title: "Investigating the possible factors affecting Canadian Individuals and Families' feelings about life"
author: 
  - Alicia Yang
  - Jiayi Du
  - Kaiyuan Yan
thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In recent years Canadian society has shown diverse attitude towards the idea of forming a family. To investigate on the reason behind this controversy, this paper conducted the research on the factors which may have an impact on single and married people’s feelings about life based on the General Social Survey(GSS). After screening and comparison, we found that the factors that may affect people’s feelings about life in the survey include age, respondent income, sex, average working hours, and education level. By observing the result, we found that single people of younger age with less income and less working hours feel happier about life, while married peole of older age with less income and less working hours and higher education level feel more satisfied with their life. Moreover, we analyzed the reason for these factors causing effect and discussed the possible bias in the research and the solutions to it."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

The General Social Survey(GSS) conducted a survey on the topic of Canadian Families in 2017 [@citeGSSdata]. By utilizing the data collected from the survey, we found that married couples are actually more likely to be happier about their lives than the singles, which contradicts to many people's perception about marriage and family. In order to understand how this controversy is formed, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, personal income, average working hours and so on. The survey data is thoroughly discussed in the section of \@ref(data). In the sub-section \@ref(dataset-of-interest), we presented an overview of the original survey data, and explained our cleaned dataset that we'll for exploration. The methods used to collect the GSS data as well as the strengths and weaknesses associated with these methods are outlined in the sub-sections \@ref(methodology), \@ref(strengths), and \@ref(weaknesses). Section \@ref(results) presents a series of findings in relation to how the different aspects we picked have impacts on single and married people’s feelings about life. These aspects include age, gender, average hours worked, respondent income, and education level. In section \@ref(discussion), a discussion is made to elaborate on the implications of the findings we've got from the survey data. Furthermore, we talked about the possible reasons that lead to the the effect of these factors on single and married people's feelings about life.

A supplementary survey is provided in the Appendix in section \@ref(appendix) that incorporate the main focus of this paper and the general social survey. It is designed to obtain more information to enhance the quality of the survey data and to pursue further investigation on this topic.

@@

## Methodology

@@

## Gender vs Feelings about life
```{r figure2, echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.5}
sex_rate <- gss %>%
  select(sex, feelings_life, marital_status) %>%
  drop_na()
ggplot(aes(x = feelings_life, fill = sex), data = sex_rate) +geom_bar(position = "dodge", binwidth = 1)+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Sex")
```

@@

@@

\newpage
```{r include=FALSE}
gss<-gss%>%na.omit(gss)
gss<-gss%>%filter(marital_status=="Married"|marital_status=="Single, never married")%>%filter(average_hours_worked!="Don't know")
```

@@

## Average weekly working hours vs Feelings about life

@@

\newpage
```{r figure4, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=4.1}
ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_bar(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")+theme_minimal()

@@

## Education vs Feelings about life

@@

\newpage
```{r figure5,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=4.8}
ggplot(gss,aes(x=feelings_life,fill=education))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")+theme_minimal()

@@

# Discussion

## Ageing and Family life

@@

@@

## Questions
```{r echo = FALSE, out.width = '70%', fig.align="center"}
knitr::include_graphics("../input/survey1.png")
knitr::include_graphics("../input/survey2.png")
```

>>>>

---
title: "Investigating the possible aspects affecting Canadian Individuals and Families' feelings about life"
author: 
  - Alicia Yang
  - Jiayi Du
  - Kaiyuan Yan
thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In recent years Canadian society has shown diverse attitude towards the idea of forming a family. To investigate on the reason behind this controversy, this paper conducted the research on the factors which may have an impact on single and married people’s feelings about life based on the General Social Survey(GSS). After screening and comparison, we found that the factors that may affect people’s feelings about life in the survey include age, respondent income, sex, average working hours, and education level. By observing the result, we found that single people of younger age with less income and less working hours feel happier about life, while married peole of older age with less income and less working hours and higher education level feel more satisfied with their life. Moreover, we analyzed the reason for these factors causing effect and discussed the possible bias in the research and the solutions to it."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

The General Social Survey(GSS) conducted a survey on the topic of Canadian Families in 2017 [@citeGSSdata]. By utilizing the data collected from the survey, we found that married couples are actually more likely to be happier about their lives than the singles, which contradicts to many people's perception about marriage and family. In order to understand how this controversy is formed, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, personal income, average working hours and so on. The survey data is thoroughly discussed in the section of \@ref(data). In the sub-section \@ref(dataset-of-interest), we presented an overview of the original survey data, and explained our cleaned dataset that we'll for exploration. The methods used to collect the GSS data as well as the strengths and weaknesses associated with these methods are outlined in the sub-sections \@ref(methodology), \@ref(strengths), and \@ref(weaknesses). Section \@ref(results) presents a series of findings in relation to how the different aspects we picked have impacts on single and married people’s feelings about life. These aspects include age, gender, average hours worked, respondent income, and education level. In section \@ref(discussion), a discussion is made to elaborate on the implications of the findings we've got from the survey data. Furthermore, we talked about the possible reasons that lead to the effect of these factors on single and married people's feelings about life.

A supplementary survey is provided in the Appendix in section \@ref(supplementary-survey) that incorporate the main focus of this paper and the general social survey. It is designed to obtain more information to enhance the quality of the survey data and to pursue further investigation on this topic.

@@

```{r figure0, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life between single and married people", fig.width=7, fig.height=3.5}
ggplot(aes(x = feelings_life), data = gss)+geom_bar()+facet_wrap(~marital_status)+ylab("number of people")+xlab("feelings about life")+theme_minimal()
```

By looking at the distribution of survey data in Figure \@ref(fig:figure0) it seems like a much larger proportion(more than 70%) of married respondents have better feelings about life, giving scores between 8 to 10, while for the single respondents, a less percentage of them give high scores between 8 to 10 of how they feel about their life. This finding is contradicting to many Canadians' attitudes towards marriage and family, which is that it is unnecessary. Therefore, we will look into how different factors that we've selected cause the difference in attitude and feelings towards marriage, and what particular characteristics of each individuals make their single/married lives better.

\newpage
## Methodology

@@

## Gender vs Feelings about life

@@

\newpage
```{r figure2, echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.5}
sex_rate <- gss %>%
  select(sex, feelings_life, marital_status) %>%
  drop_na()
ggplot(aes(x = feelings_life, fill = sex), data = sex_rate) +geom_bar(position = "dodge", binwidth = 1)+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Sex")
```

@@

```{r include=FALSE}
gss<-gss%>%na.omit(gss)
gss<-gss%>%filter(marital_status=="Married"|marital_status=="Single, never married")%>%filter(average_hours_worked!="Don't know")
```

@@

\newpage
## Average weekly working hours vs Feelings about life

@@

```{r figure4, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=4.1}
ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_bar(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")+theme_minimal()

@@

\newpage
## Education vs Feelings about life

@@

```{r figure5,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=4.8}
ggplot(gss,aes(x=feelings_life,fill=education))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")+theme_minimal()

@@

\newpage
# Discussion

## Age

@@

One possible bias in relation to this result is that as we seen in Figure \@ref(fig:figure5), education levels higher than Bachelor's degree is not an option in the survey, which means that respondents with higher degrees are not included in the discussion here. We will take account of this potential bias in the supplementary survey provided at the end of the paper.

@@

## Questions
```{r echo = FALSE, out.width = '70%', fig.align="center"}
knitr::include_graphics("../input/survey1.png")
knitr::include_graphics("../input/survey2.png")
knitr::include_graphics("../input/survey3.png")
knitr::include_graphics("../input/survey4.png")
knitr::include_graphics("../input/survey5.png")
knitr::include_graphics("../input/survey6.png")
knitr::include_graphics("../input/survey7.png")
knitr::include_graphics("../input/survey8.png")
knitr::include_graphics("../input/survey9.png")
```
